Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-24 automatica/paper.tex
new template

% autosam.tex
% Annotated sample file for the preparation of LaTeX files
% for the final versions of papers submitted to or accepted for 
% publication in AUTOMATICA.

% See also the Information for Authors.

% Make sure that the zip file that you send contains all the 
% files, including the files for the figures and the bib file.

% Output produced with the elsart style file does not imitate the
% AUTOMATICA style. The style file is generic for all Elsevier
% journals and the output is laid out for easy copy editing. The
% final document is produced from the source file in the
% AUTOMATICA style at Elsevier.

% You may use the style file autart.cls to obtain a two-column 
% document (see below) that more or less imitates the printed 
% Automatica style. This may helpful to improve the formatting 
% of the equations, tables and figures, and also serves to check 
% whether the paper satisfies the length requirements.

% Please note: Authors must not create their own macros.

% For further information regarding the preparation of LaTeX files 
% for Elsevier, please refer to the "Full Instructions to Authors" 
% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
% directory pub/styles, or from the internet (CTAN sites) on
% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
% tex-archive/macros/latex/contrib/supported/elsevier.

%\documentclass{elsart}               % The use of LaTeX2e is preferred.

\documentclass[twocolumn]{autart}    % Enable this line and disable the 
                                     % preceding line to obtain a two-column 
                                     % document whose style resembles the
                                     % printed Automatica style.

@@

%\newcommand{\tool}{{\sf DSSynth}\xspace}
\newcommand{\addtodo}[1]{\textcolor{red}{[#1]}}
\newcommand{\mat}[1]{{#1}}
\renewcommand{\vec}[1]{{#1}}
\newcommand{\comment}[1]{}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{proof}{Proof}

@@

\begin{document}
\newcommand\tool{{\sf DSSynth}}
\begin{frontmatter}

@@

%\thanks[footnoteinfo]{This paper was not presented at any IFAC 
%meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
%Fax +XXXIX-VI-mmmxxv.}

\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@cs.ox.ac.uk},
\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@cs.ox.ac.uk}

\address[oxford]{University of Oxford, UK}
\address[cambridge]{University of Cambridge, UK}
\address[manchester]{University of Manchester, UK}
\address[manaus]{Federal University of Amazonas, Brazil}

\begin{keyword}                           % Five to ten keywords,  
Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Time sampling.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\end{frontmatter}

@@

\bibliographystyle{plain}        % Include this if you use bibtex 
\bibliography{paper}           % and a bib file to produce the 
                                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

@@

%\newcommand{\tool}{{\sf DSSynth}\xspace}
\newcommand{\addtodo}[1]{\textcolor{red}{[#1]}}
\newcommand{\mat}[1]{{#1}}
\renewcommand{\vec}[1]{{#1}}
\newcommand{\comment}[1]{}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proof}{Proof}

@@

\begin{document}
\newcommand\tool{{\sf DSSynth}}

@@

\author{Alessandro Abate         \and
        Iury Bessa \and
        Dario Cattaruzza \and
        Lucas Cordeiro \and
        Cristina David \and
        Pascal Kesseli \and
        Daniel Kroening \and
        Elizabeth Polgreen
}

\authorrunning{Abate et al.} % if too long for running head

%\institute{F. Author \at
%              first address \\
%
%              \email{fauthor@example.com}           %  \\
%%             \emph{Present address:} of F. Author  %  if needed
%           \and
%           S. Author \at
%              second address
%}

\maketitle
%\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
%\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
%\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
%\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
%\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
%\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@cs.ox.ac.uk},
%\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
%\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@cs.ox.ac.uk}
%
%\address[oxford]{University of Oxford, UK}
%\address[cambridge]{University of Cambridge, UK}
%\address[manchester]{University of Manchester, UK}
%\address[manaus]{Federal University of Amazonas, Brazil}

\keywords{                        % Five to ten keywords,  
Digital control synthesis \and Safety requirements \and Analog/Digital conversion \and Quantization errors \and Time sampling              % chosen from the IFAC 
}                            % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

@@

\bibliographystyle{spbasic}       % Include this if you use bibtex 
\bibliography{paper}           % and a bib file to produce the 
                                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.
